### 2023-12-04 Response.md
WIP: response

# Response

## Comments from the reviewer

评审员指出，在回应2中，作者提到“实际上，无论是细胞表面还是凸包，在计算机上我们处理的都是它们的离散点。”评审员接着解释，有限点集的凸包是多面体（有界多面体），其边界是非光滑的。此外，手稿中写道：“凸包为进一步分析提供了两个重要信息：包含整个细胞表面的最小凸多面体...”，因此在这一点上作者和评审员似乎是一致的。

作者在回应中继续说：“换句话说，我们可以理解这些离散点是其真实连续光滑函数上的采样值。”评审员提出假设，将M和N（细胞表面和其凸包的真实边界）视为光滑流形。然后，他们将计算机上找到的离散点的凸包边界称为Q。这不是一个光滑流形。因此，即使可以将第3.1、3.3和3.4节的理论直接应用于M和N，但不能应用于Q。换句话说，Q只是N的多面体近似。任何近似都伴随着近似误差和其他在手稿中被忽视的问题。评审员建议在手稿中添加有关这个问题的评论。

此外，评审员指出，先前章节的理论和第3.6节中描述的实现之间存在明显差距。顺便说一下，第3.6节非常简短，且在算法1的子程序中隐藏了许多重要的实现细节。也许这就是为什么作者不得不在回应3和4中向评审员解释这些细节。但这些细节应该包含在手稿中！

## Response to the comments

谢谢评审员的建议！的确，在进行实际计算时候，细胞表面是离散点构成的三角网格，而凸包是由这些离散点构成的多面体，所以理论分析部分不能直接用于实际计算。我们决定通过remark 3.1来解释这个问题，因为虽然实际参与计算的细胞表面和凸包都不是光滑流形，但是他们却是真实的细胞表面流形和凸包流形的近似。再根据映射的连续性，我们可以得到实际计算中的细胞表面和凸包的近似误差。我们在remark 3.1中给出了这个误差的上界。

<!-- Remark 3.1: Suppose that the surface of a cell is a smooth manifold $M$ and its convex hull is a smooth manifold $N$. Let $P$ be the discrete surface of the cell and $Q$ be the discrete convex hull of the cell.  -->

<!-- Consider the map $f_\theta: M \rightarrow P$ and $g_{\theta}: N \rightarrow Q$ which map the smooth manifolds to their discrete approximations, where $\theta$ and $\theta'$ are the parameters of the discrete approximation.

In this procedure, because of the property of discrete approximation, $\forall \epsilon > 0$, $\exists \theta > 0$, such that $\forall x_1 \in M$ and $x -->

Denote the cateogry of $3$-dimensional manifolds as $\mathcal{M}$, and the convex-hull morphism $f$ is defined as
$$
\begin{aligned}
f: \mathcal{M} &\rightarrow \mathcal{M} \\
M &\mapsto N
\end{aligned}
$$ where $N$ is the convex hull of $M$. Then $f$ is a smooth morphism/diffeomorphism.

Consider the discrete approximation of any $M \in \mathcal{M}$, denoted as $P$. Regardless how $d$ is concretely define, as far as $d$ is a distance on $\mathcal{M}$, then given a manifold $M$, $\forall \epsilon > 0$, there exists a $g_\theta$ such that $d(M, g_\theta(M)) < \epsilon$, where $g_\theta$ is the discrete approximation and $\theta$ is the parameter of the discrete approximation.

Now suppose that the surface of a cell is a smooth manifold $M$ and its convex hull is a smooth manifold $N$. Let $P$ be the discrete surface of the cell and $Q$ be the discrete convex hull of the cell.

$\forall \epsilon > 0$, $\exists \theta > 0$, such that $d(M, P) < \epsilon_1$, where $P = g_\theta(M)$ and $g_\theta$ is the discrete approximation of $M$.

And denote the discrete approximation of $N$ as $Q' = g_{\theta}(N)$, then $d(N, Q') < \epsilon_2$.

Then we have $d(P, Q') < \epsilon_1 + \epsilon_2$.

### 2023-12-06 response/gpt.tex
response draft

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\title{Exploring Discrete Approximations of Manifolds in Computational Geometry}
\author{Author Name}
\date{}

\begin{document}

\maketitle

\section{Introduction}
In this paper, we delve into the relationship between continuous manifolds and their discrete approximations, particularly focusing on the mesh functor \( g_\theta \) and its role in computational geometry.

\section{Mesh Functor \( g_\theta \) and its Properties}
The mesh functor \( g_\theta \), given a parameter \( \theta \), discretizes a continuous manifold \( M \) into a finite triangular mesh \( P \). This process is crucial in computational applications where exact manifold representations are infeasible.

\subsection{Definition and Continuity}
The functor \( g_\theta \) can be formally defined as follows:
\[ g_\theta : \mathbf{Man} \rightarrow \mathbf{SimpCplx} \]
where \( \mathbf{Man} \) denotes the category of 3-dimensional manifolds and \( \mathbf{SimpCplx} \) the category of simplicial complexes. This functor preserves essential topological and geometric features of \( M \), albeit in a discretized form.

\subsection{Error Analysis}
An important aspect of \( g_\theta \) is the error introduced during the discretization. The Gromov-Hausdorff distance provides a measure of this error, offering insights into the fidelity of \( P \) as an approximation of \( M \).

\section{Comparative Analysis}
\subsection{Manifold \( M \) versus Mesh \( P \)}
The fidelity of \( P \) in representing \( M \) is crucial for algorithms in computational geometry. Despite the inherent approximation, \( P \) maintains most of the critical geometric properties of \( M \), allowing for effective algorithmic processing.

\subsection{Algorithmic Considerations}
The discrete nature of \( P \) introduces unique computational challenges and opportunities. Algorithms must be adapted to handle the discrete structure efficiently, balancing accuracy and computational complexity.

\section{Conclusion}
Our exploration underscores the significance of the mesh functor \( g_\theta \) in bridging the gap between theoretical manifolds and their practical computational counterparts. This understanding is pivotal for advancing methods in computational geometry and related fields.

\end{document}

### 2024-01-21 Canada/Response.md
rearrange

--- 2023-12-04 Response.md
@@
 
-$\forall \epsilon > 0$, $\exists \theta > 0$, such that $d(M, P) < \epsilon_1$, where $P = g_\theta(M)$ and $g_\theta$ is the discrete approximation of $M$.
+$\forall \epsilon_1 > 0$, $\exists \theta > 0$, such that $d(M, P) < \epsilon_1$, where $P = g_\theta(M)$ and $g_\theta$ is the discrete approximation of $M$.
 
-And denote the discrete approximation of $N$ as $Q' = g_{\theta}(N)$, then $d(N, Q') < \epsilon_2$.
+And denote the discrete approximation of $N$ as $Q' = g_{\theta}(N)$, then also for the given $\epsilon_2 > 0$, there exists an $\delta > 0$, such that $d(N, Q') < \epsilon_2$.
+As far as $\epsilon_1 < \delta$, then $d(M, P) < \epsilon_1 < \delta$, and $d(N, Q') < \epsilon_2$.
+Then we have $d(P, Q') < \epsilon_2$.
 
-Then we have $d(P, Q') < \epsilon_1 + \epsilon_2$.
+And for the other way, since $Q = f(P)$, then $d(Q, Q') < \epsilon_3$
+
+$$
+\begin{aligned}

### 2024-06-17 Canada/Response.md
add comment

@@
+---
+toc: true
+documentclass: "ctexart"
+classoption: "UTF8"
+---
 # Response
-
 ## Comments from the reviewer
-
 评审员指出，在回应2中，作者提到“实际上，无论是细胞表面还是凸包，在计算机上我们处理的都是它们的离散点。”评审员接着解释，有限点集的凸包是多面体（有界多面体），其边界是非光滑的。此外，手稿中写道：“凸包为进一步分析提供了两个重要信息：包含整个细胞表面的最小凸多面体...”，因此在这一点上作者和评审员似乎是一致的。
-
 作者在回应中继续说：“换句话说，我们可以理解这些离散点是其真实连续光滑函数上的采样值。”评审员提出假设，将M和N（细胞表面和其凸包的真实边界）视为光滑流形。然后，他们将计算机上找到的离散点的凸包边界称为Q。这不是一个光滑流形。因此，即使可以将第3.1、3.3和3.4节的理论直接应用于M和N，但不能应用于Q。换句话说，Q只是N的多面体近似。任何近似都伴随着近似误差和其他在手稿中被忽视的问题。评审员建议在手稿中添加有关这个问题的评论。
-
 此外，评审员指出，先前章节的理论和第3.6节中描述的实现之间存在明显差距。顺便说一下，第3.6节非常简短，且在算法1的子程序中隐藏了许多重要的实现细节。也许这就是为什么作者不得不在回应3和4中向评审员解释这些细节。但这些细节应该包含在手稿中！
-
 ## Response to the comments
-
 谢谢评审员的建议！的确，在进行实际计算时候，细胞表面是离散点构成的三角网格，而凸包是由这些离散点构成的多面体，所以理论分析部分不能直接用于实际计算。我们决定通过remark 3.1来解释这个问题，因为虽然实际参与计算的细胞表面和凸包都不是光滑流形，但是他们却是真实的细胞表面流形和凸包流形的近似。再根据映射的连续性，我们可以得到实际计算中的细胞表面和凸包的近似误差。我们在remark 3.1中给出了这个误差的上界。
-
 <!-- Remark 3.1: Suppose that the surface of a cell is a smooth manifold $M$ and its convex hull is a smooth manifold $N$.
@@
 -->
-
 <!-- Consider the map $f_\theta: M \rightarrow P$ and $g_{\theta}: N \rightarrow Q$ which map the smooth manifolds to their discrete approximations, where $\theta$ and $\theta'$ are the parameters of the discrete approximation.
-
 In this procedure, because of the property of discrete approximation, $\forall \epsilon > 0$, $\exists \theta > 0$, such that $\forall x_1 \in M$ and $x -->
-
 Denote the cateogry of $3$-dimensional manifolds as $\mathcal{M}$, and the convex-hull morphism $f$ is defined as
@@
 $$ where $N$ is the convex hull of $M$. Then $f$ is a smooth morphism/diffeomorphism.
-
 Consider the discrete approximation of any $M \in \mathcal{M}$, denoted as $P$.
 Regardless how $d$ is concretely define, as far as $d$ is a distance on $\mathcal{M}$, then given a manifold $M$, $\forall \epsilon > 0$, there exists a $g_\theta$ such that $d(M, g_\theta(M)) < \epsilon$, where $g_\theta$ is the discrete approximation and $\theta$ is the parameter of the discrete approximation.
-
 Now suppose that the surface of a cell is a smooth manifold $M$ and its convex hull is a smooth manifold $N$.
 Let $P$ be the discrete surface of the cell and $Q$ be the discrete convex hull of the cell.
-
 $\forall \epsilon_1 > 0$, $\exists \theta > 0$, such that $d(M, P) < \epsilon_1$, where $P = g_\theta(M)$ and $g_\theta$ is the discrete approximation of $M$.
-
 And denote the discrete approximation of $N$ as $Q' = g_{\theta}(N)$, then also for the given $\epsilon_2 > 0$, there exists an $\delta > 0$, such that $d(N, Q') < \epsilon_2$.
@@
 Then we have $d(P, Q') < \epsilon_2$.
-
 And for the other way, since $Q = f(P)$, then $d(Q, Q') < \epsilon_3$
-
 $$

### 2024-06-17 add_ctexart_comment.py
math equations

@@ -1,0 +1,42 @@
+import glob
+
+###
+ # File: /add_ctexart_comment.py
+ # Created Date: Monday, June 17th 2024
+ # Author: Zihan
+ # -----
+ # Last Modified: Monday, 17th June 2024 4:31:23 pm
+ # Modified By: the developer formerly known as Zihan at <wzh4464@gmail.com>
+ # -----
+ # HISTORY:
+ # Date      		By   	Comments
+ # ----------		------	---------------------------------------------------------
+###
+
+# Find all Markdown files recursively
+md_files = glob.glob('**/*.md', recursive=True)
+
+# Comment to be added
+comment = '''---
+toc: true
+documentclass: "ctexart"
+classoption: "UTF8"
+---
+'''
+
+# Add the comment to each file
+for file in md_files:
+  with open(file, 'r+') as f:
+    content = f.read()
+    f.seek(0, 0)
+    f.write(comment + content)
+
+# delete first blank lines
+# for file in md_files:
+#   with open(file, 'r+') as f:
+#     content = f.readlines()
+#     f.seek(0, 0)
+#     for line in content:
+#       if line.strip() != '':
+#         f.write(line)
+#     f.truncate()

### 2024-06-17 Canada/Response.md

--- 2023-12-04 Response.md
@@
+---
+toc: true
+documentclass: "ctexart"
+classoption: "UTF8"
+---
 # Response
@@
 评审员指出，在回应2中，作者提到“实际上，无论是细胞表面还是凸包，在计算机上我们处理的都是它们的离散点。”评审员接着解释，有限点集的凸包是多面体（有界多面体），其边界是非光滑的。此外，手稿中写道：“凸包为进一步分析提供了两个重要信息：包含整个细胞表面的最小凸多面体...”，因此在这一点上作者和评审员似乎是一致的。
-
 作者在回应中继续说：“换句话说，我们可以理解这些离散点是其真实连续光滑函数上的采样值。”评审员提出假设，将M和N（细胞表面和其凸包的真实边界）视为光滑流形。然后，他们将计算机上找到的离散点的凸包边界称为Q。这不是一个光滑流形。因此，即使可以将第3.1、3.3和3.4节的理论直接应用于M和N，但不能应用于Q。换句话说，Q只是N的多面体近似。任何近似都伴随着近似误差和其他在手稿中被忽视的问题。评审员建议在手稿中添加有关这个问题的评论。
-
 此外，评审员指出，先前章节的理论和第3.6节中描述的实现之间存在明显差距。顺便说一下，第3.6节非常简短，且在算法1的子程序中隐藏了许多重要的实现细节。也许这就是为什么作者不得不在回应3和4中向评审员解释这些细节。但这些细节应该包含在手稿中！
@@
 谢谢评审员的建议！的确，在进行实际计算时候，细胞表面是离散点构成的三角网格，而凸包是由这些离散点构成的多面体，所以理论分析部分不能直接用于实际计算。我们决定通过remark 3.1来解释这个问题，因为虽然实际参与计算的细胞表面和凸包都不是光滑流形，但是他们却是真实的细胞表面流形和凸包流形的近似。再根据映射的连续性，我们可以得到实际计算中的细胞表面和凸包的近似误差。我们在remark 3.1中给出了这个误差的上界。
-
-<!-- Remark 3.1: Suppose that the surface of a cell is a smooth manifold $M$ and its convex hull is a smooth manifold $N$.
-Let $P$ be the discrete surface of the cell and $Q$ be the discrete convex hull of the cell.
+<!-- Remark 3.1: Suppose that the surface of a cell is a smooth manifold$M$and its convex hull is a smooth manifold$N$.
+Let$P$be the discrete surface of the cell and$Q$be the discrete convex hull of the cell.
 -->
-
-<!-- Consider the map $f_\theta: M \rightarrow P$ and $g_{\theta}: N \rightarrow Q$ which map the smooth manifolds to their discrete approximations, where $\theta$ and $\theta'$ are the parameters of the discrete approximation.
-
-In this procedure, because of the property of discrete approximation, $\forall \epsilon > 0$, $\exists \theta > 0$, such that $\forall x_1 \in M$ and $x -->
-
-Denote the cateogry of $3$-dimensional manifolds as $\mathcal{M}$, and the convex-hull morphism $f$ is defined as
+<!-- Consider the map$f_\theta: M \rightarrow P$and$g_{\theta}: N \rightarrow Q$which map the smooth manifolds to their discrete approximations, where$\theta$and$\theta'$are the parameters of the discrete approximation.
+In this procedure, because of the property of discrete approximation,$\forall \epsilon > 0$,$\exists \theta > 0$, such that$\forall x_1 \in M$and$x -->
+Denote the cateogry of$3$-dimensional manifolds as$\mathcal{M}$, and the convex-hull morphism$f$is defined as
 $$
@@
 \end{aligned}
-$$ where $N$ is the convex hull of $M$. Then $f$ is a smooth morphism/diffeomorphism.
-
-Consider the discrete approximation of any $M \in \mathcal{M}$, denoted as $P$.
-Regardless how $d$ is concretely define, as far as $d$ is a distance on $\mathcal{M}$, then given a manifold $M$, $\forall \epsilon > 0$, there exists a $g_\theta$ such that $d(M, g_\theta(M)) < \epsilon$, where $g_\theta$ is the discrete approximation and $\theta$ is the parameter of the discrete approximation.
-
-Now suppose that the surface of a cell is a smooth manifold $M$ and its convex hull is a smooth manifold $N$.
-Let $P$ be the discrete surface of the cell and $Q$ be the discrete convex hull of the cell.
-
-$\forall \epsilon > 0$, $\exists \theta > 0$, such that $d(M, P) < \epsilon_1$, where $P = g_\theta(M)$ and $g_\theta$ is the discrete approximation of $M$.
-
-And denote the discrete approximation of $N$ as $Q' = g_{\theta}(N)$, then $d(N, Q') < \epsilon_2$.
-
-Then we have $d(P, Q') < \epsilon_1 + \epsilon_2$.
+$$where$N$is the convex hull of$M$. Then$f$is a smooth morphism/diffeomorphism.
+Consider the discrete approximation of any$M \in \mathcal{M}$, denoted as$P$.
+Regardless how$d$is concretely define, as far as$d$is a distance on$\mathcal{M}$, then given a manifold$M$,$\forall \epsilon > 0$, there exists a$g_\theta$such that$d(M, g_\theta(M)) < \epsilon$, where$g_\theta$is the discrete approximation and$\theta$is the parameter of the discrete approximation.
+Now suppose that the surface of a cell is a smooth manifold$M$and its convex hull is a smooth manifold$N$. Let$P$be the discrete surface of the cell and$Q$be the discrete convex hull of the cell.
+$\forall \epsilon_1 > 0$,$\exists \theta > 0$, such that$d(M, P) < \epsilon_1$, where$P = g_\theta(M)$and$g_\theta$is the discrete approximation of$M$.
+And denote the discrete approximation of$N$as$Q' = g_{\theta}(N)$, then also for the given$\epsilon_2 > 0$, there exists an$\delta > 0$, such that$d(N, Q') < \epsilon_2$.
+As far as$\epsilon_1 < \delta$, then$d(M, P) < \epsilon_1 < \delta$, and$d(N, Q') < \epsilon_2$.
+Then we have$d(P, Q') < \epsilon_2$.
+And for the other way, since$Q = f(P)$, then$d(Q, Q') < \epsilon_3$
+$$
+\begin{aligned}

### 2024-06-17 add_ctexart_comment.py
script

@@ -1,11 +1,12 @@
 import glob
+import os
 
 ###
  # File: /add_ctexart_comment.py
  # Created Date: Monday, June 17th 2024
  # Author: Zihan
  # -----
- # Last Modified: Monday, 17th June 2024 4:31:23 pm
+ # Last Modified: Monday, 17th June 2024 7:53:50 pm
  # Modified By: the developer formerly known as Zihan at <wzh4464@gmail.com>
  # -----
  # HISTORY:
@@ -17,19 +18,19 @@ import glob
 md_files = glob.glob('**/*.md', recursive=True)
 
 # Comment to be added
-comment = '''---
-toc: true
-documentclass: "ctexart"
-classoption: "UTF8"
----
-'''
+# comment = '''---
+# toc: true
+# documentclass: "ctexart"
+# classoption: "UTF8"
+# ---
+# '''
 
 # Add the comment to each file
-for file in md_files:
-  with open(file, 'r+') as f:
-    content = f.read()
-    f.seek(0, 0)
-    f.write(comment + content)
+# for file in md_files:
+#   with open(file, 'r+') as f:
+#     content = f.read()
+#     f.seek(0, 0)
+#     f.write(comment + content)
 
 # delete first blank lines
 # for file in md_files:
@@ -40,3 +41,16 @@ for file in md_files:
 #       if line.strip() != '':
 #         f.write(line)
 #     f.truncate()
+
+# substitute all space in file name with '_'
+# for file in md_files:
+#   new_file = file.replace(' ', '_')
+#   print(f'Renaming {file} to {new_file}')
+#   os.rename(file, new_file)
+
+# also for foler name
+folders = glob.glob('**/', recursive=True)
+for folder in folders:
+  new_folder = folder.replace(' ', '_')
+  print(f'Renaming {folder} to {new_folder}')
+  os.rename(folder, new_folder)

### 2024-06-17 add_ctexart_comment.py
1.0.3

@@ -6,7 +6,7 @@ import os
  # Created Date: Monday, June 17th 2024
  # Author: Zihan
  # -----
- # Last Modified: Monday, 17th June 2024 7:53:50 pm
+ # Last Modified: Monday, 17th June 2024 7:59:27 pm
  # Modified By: the developer formerly known as Zihan at <wzh4464@gmail.com>
  # -----
  # HISTORY:
@@ -43,14 +43,14 @@ md_files = glob.glob('**/*.md', recursive=True)
 #     f.truncate()
 
 # substitute all space in file name with '_'
-# for file in md_files:
-#   new_file = file.replace(' ', '_')
-#   print(f'Renaming {file} to {new_file}')
-#   os.rename(file, new_file)
+for file in md_files:
+  new_file = file.replace(' ', '_')
+  print(f'Renaming {file} to {new_file}')
+  os.rename(file, new_file)
 
 # also for foler name
-folders = glob.glob('**/', recursive=True)
-for folder in folders:
-  new_folder = folder.replace(' ', '_')
-  print(f'Renaming {folder} to {new_folder}')
-  os.rename(folder, new_folder)
+# folders = glob.glob('**/', recursive=True)
+# for folder in folders:
+#   new_folder = folder.replace(' ', '_')
+#   print(f'Renaming {folder} to {new_folder}')
+#   os.rename(folder, new_folder)
